---
output:
  github_document:
    html_preview: true
    toc: false
    fig_width: 8
    fig_height: 8
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

<!-- badges: start -->
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/ggwrap)](https://cran.r-project.org/package=ggwrap)
[![Lifecycle: deprecated](https://img.shields.io/badge/lifecycle-deprecated-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#deprecated)
<!-- badges: end -->

# This package is no longer maintained

Use [`ggbreak::scale_wrap()`](https://cran.r-project.org/web/packages/ggbreak/vignettes/ggbreak.html#wrap-plot) instead.

# ggwrap

'ggwrap' wraps a 'ggplot2' plot over multiple rows, to make plots with long x axes easier to read.

# Installation

The development version of 'ggwrap' can be installed from GitHub:

```{r eval = F}
devtools::install_github("wilkox/ggwrap")
```

# Usage

The `ggwrap` function takes two arguments: a 'ggplot2' plot, and the number of
rows over which the plot should be wrapped.

Here's a simple plot.

```{r}
library(ggplot2)
library(ggwrap)
plot <- ggplot(economics, aes(x = date, y = unemploy, colour = uempmed)) +
  geom_line()
plot
```

We can use `ggwrap` to wrap the plot over four rows.

```{r}
ggwrap(plot, 4)
```
